---
title       : How much is the diamond?
subtitle    : Predict the price for a given weight with linear Regression Model
author      : Steven Fu
job         : Software Developer
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction (Slide 2)

How much is the diamond?

This Shiny App is to display the relationship of weight and price of diamond, and to provide prediction of price for a given weight using linear regession.

For a copy of the Shiny App:

-URL: https://stevenfupc.shinyapps.io/devdataprod-011/

-GitHub: https://github.com/StevenFupc/devdataprod-011

---
## Take a look at the dataset (Slide 3)

The diamond dataset is from the build-in dataset.
To get the data use library(UsingR); data(diamond).

Take a look the dataset:
```{r dataset, warning=FALSE}
    library(UsingR)
    data(diamond)
    str(diamond)
```

--- 
## Regression Model (Slide 4)
The relationship of price and weight is shown below(linear regression).

```{r plot, warning=FALSE, echo=FALSE}
    library(UsingR)
    data(diamond)
    plot(diamond$carat,diamond$price, xlab="Mass(carats)", ylab="Price(SIN$)",
         bg="lightblue",col="black",cex=1.1,pch=21,frame=FALSE)
    abline(lm(price~carat,data=diamond),lwd=2)
```

--- 
## Prediction (Slide 5)
User enters a weight in carats (0.15 - 0.35).
The app will predict the price and the range using linear regression model.
For example, user enters 0.20 as weight.
```{r predict, warning=FALSE}
library(UsingR)
data(diamond)
fit <- lm(price ~ carat, data = diamond)
values<-predict(fit, newdata = data.frame(carat = 0.20 ), interval = "prediction")
values
```
The `r values[1]` is the predicted price; 
and `r values[2]` ~ `r values[3]` is the predicted range.

